### 2013-09-25 evaluation/paper.tex
working on approximate inference result discussion

\subsection{Experiments using Approximate Inference}
For the remaining tasks of the snakes dataset and image segmentation, exact
inference is intractable for learning.

We use two different approximate inference algorithms, fusion moves, a fast
local search procedure, and the linear programming relaxation provided by AD$^3$,
not using branch-and-bound.

Evaluation of algorithms where exact inference is not possible is much harder,
as it is usually not possible to evaluate the exact objective. When using AD$^3$,
we can still consider the relaxed task, which will be solved exactly in the
majority of cases (AD$^3$ can fail to find the primal solution to the LP
relaxation).
When using fusion moves, there is no obvious interpretation of the produced
primal objective, other than that it provides a lower bound of the actual
objective. Nevertheless, we find it informative to analyze the behavior of this
lower bound.

@@

\Figref{snakes_results} shows the results on the snakes dataset.
The top row shows the objective when learning with fusion-moves, the next row the training set loss.
First, we notice that even the approximate

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time_loss}
    \end{tabu}
\caption{%
    Results on the snakes dataset. The top four plots show results using fusion
    move inference, the bottom four plots using AD$^3$. The training set error shows
    that none of the algorithms is able to solve the task using fusion moves.
    The objective values for fusion move inference are only approximate, giving
    an upper bound on the true primal objective, while the objective for AD$^3$
    is the true objective for the relaxed task.
\figlabel{snakes_results}}
\end{figure}

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/msrc}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/msrc_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/pascal}&%
    \includegraphics[width=\linewidth]{evaluation/images/pascal_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/pascal_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/pascal_time_loss}
    \end{tabu}
\caption{%
    Objective and traning set loss on the segmentation task. The top four plots
    show results for the MSRC-21 dataset, the bottom four plots for the Pascal
    VOC dataset. As approximate inference was used, the shown objective values
    are only lower bounds on the actual primal objective.
\figlabel{msrc_pascal}}
\end{figure}

@@

With respect to approximate learning, we found that the inference algorithm has
a stronger impact on the performance than the learning algorithm.
While the SSGD and SZLJSP algorithms have somewhat lower training error on the snakes than
the cutting-plane algorithm when using fusion-move inference, they, too, fail at solving the task.
Using the linear programming relaxation, on the other hand, all algorithms are able to solve the
task near perfect.
For the segmentation datasets, the approximate inference seem to be less of a
problem, as most algorithms achieve the desired approximate duality gap (which
is not the actual duality gap, see Chapter~\ref{ch:exact_learning} for a
discussion).
The large label space made using the linear programming relaxation intractable,
though, and we can not draw a final conclusion here. In the next chapter,
Chapter~\ref{ch:exact_learning}, we will demonstrate how we can learn exactly,
even in this setting.

>>>>

\subsection{Experiments using Approximate Inference}
For the remaining tasks, the snakes dataset and image segmentation, exact
inference is intractable for learning.
%
We use two different approximate inference algorithms, fusion moves, a fast
local search procedure, and the linear programming relaxation provided by AD$^3$,
not using branch-and-bound, in contrast to the multi-label setup above.

Evaluation of algorithms where exact inference is not possible is much harder,
as it is usually not possible to evaluate the exact objective. When using AD$^3$,
we can still consider the relaxed task, which will be solved exactly in the
majority of cases (AD$^3$ can fail to find the primal solution to the LP
relaxation).
When using fusion moves, there is no obvious interpretation of the approximate
primal objective, other than that it provides a lower bound of the actual
objective. Nevertheless, we find it informative to analyze the behavior of this
lower bound. In contrast to the previous section, we show primal and dual objective
values instead of the primal suboptimality when using approximate inference.
The dual values do provide lower bounds
to the exact objective, and are therefore somewhat more informative here, see
Chapter~\ref{ch:exact_learning} for a discussion.

@@

\Figref{snakes_results} shows the results on the snakes dataset.
The top row shows the objective when learning with fusion-moves, the next row
the training set loss.  First, we observe that using fusion-moves even the
approximate objective does not reach the desired optimality gap for the
$1$-slack and SZLJSP algorithms. This is caused by the algorithms not finding
any further constraints. The $n$-slack algorithm fairs a bit better and
achieves a higher dual value. Looking at the loss, it is clear that the stochastic
algorithms have an advantage, possibly caused by not breaking to early.
Still all algorithms ultimately fail to solve the task.

The situation is very different when using the linear programming relaxation.
Looking at the four plots at the bottom of \Figref{snakes_results}, we see that all
algorithms are able to solve the task perfectly. %FIXME more details!
Surprisingly, SSGD was very successful on this dataset, even faster then the non-caching $n$-slack
algorithm. Caching provides nearly an order of magnitude speed-up on the dataset.

Using branch-and-bound to obtain exact results was not feasible on this dataset.

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time_loss}
    \end{tabu}
\caption{%
    Results on the snakes dataset. The top four plots show results using fusion
    move inference, the bottom four plots using AD$^3$. Dashed lines indicate the dual objective.
\figlabel{snakes_results}}
\end{figure}

The last set of experiments is on the segmentation dataset MSRC-21 and Pascal
VOC\@.  Because of the large number of labels and samples, it is only feasible
to use the fusion move inference algorithms. The results are shown in
figure~\cite{msrc_pascal_curves}, with the top four plots showing results on
MSRC-21, and the bottom four plots showing results on Pascal VOC.

In both datasets, the $1$-slack algorithm is somewhat slow in minimizing the
training set error, and the $n$-slack and stochastic algorithms are much
faster. All algorithms achieve the desired suboptimality, at least in the
approximate objective. This suggests that inference is somewhat easier for this
task.

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/msrc}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/msrc_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/pascal}&%
    \includegraphics[width=\linewidth]{evaluation/images/pascal_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/pascal_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/pascal_time_loss}
    \end{tabu}
\caption{%
    Objective and traning set loss on the segmentation task. The top four plots
    show results for the MSRC-21 dataset, the bottom four plots for the Pascal
    VOC dataset.
\figlabel{msrc_pascal_curves}}
\end{figure}

@@

With respect to approximate learning, we found that the inference algorithm has
a stronger impact on the performance than the learning algorithm.
While the SSGD and SZLJSP algorithms have somewhat lower training error on the snakes than
the cutting-plane algorithm when using fusion-move inference, they, too, fail at solving the task.
Using the linear programming relaxation, on the other hand, all algorithms are able to solve the
task near perfect.
For the segmentation datasets, the approximate inference seem to be less of a
problem, as most algorithms achieve the desired approximate duality gap (which
is not the actual duality gap, see Chapter~\ref{ch:exact_learning} for a
discussion).
In the next chapter, Chapter~\ref{ch:exact_learning}, we will demonstrate how
we can learn exactly, even in this setting.
